Supplementary material to ``Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data''

### 2015-06-16 draft_lm1.tex
added citations suggested by the reviewer. closes #24

Dengue is an arthropod-borne febrile disease caused by a flavivirus with four 
serotypes which causes an estimated  $50$ million infections each 
year~\citep{Guzman2010}.
In humans, immunity against a particular serotype is considered permanent 
after the exposure and cross immunity to other serotypes is considered short 
lived~\citep{halstead_dengue_2007}.
As a consequence, the proportions of viral serotypes co-circulating at any 
point in time are strongly dependent on previous incidence patterns of the 
disease, which determine the number of individuals susceptible to each serotype 
at any point in time.
% LM: Maybe a citation here?

>>>>

Dengue is an arthropod-borne febrile disease caused by a flavivirus with four 
serotypes which causes an estimated  $50$ million infections each 
year~\citep{Guzman2010}.
In humans, immunity against a particular serotype is considered permanent 
after the exposure and cross immunity to other serotypes is considered short 
lived~\citep{halstead_dengue_2007} although some 
studies argue for a longer duration of cross-immunity \citep{Reich2013, 
salje2012}.
As a consequence, the proportions of viral serotypes co-circulating at any 
point in time are strongly dependent on previous incidence patterns of the 
disease, which determine the number of individuals susceptible to each serotype 
at any point in time.
% LM: Maybe a citation here?

### 2015-06-16 scirep_version.tex
added citations suggested by the reviewer. closes #24

Dengue is an arthropod-borne febrile disease caused by a flavivirus with four 
serotypes which causes an estimated  $50$ million infections each 
year~\cite{Guzman2010}.
In humans, immunity against  a particular serotype is  considered permanent 
after the exposure and cross immunity to there serotypes is considered short 
lived~\cite{halstead_dengue_2007}.
As a consequence, the proportions of viral serotypes co-circulating at any 
point in time are strongly dependent on previous incidence patterns of the 
disease, which determine the number of individuals susceptible to each serotype 
at any point in time.
% LM: Maybe a citation here?

@@

\newpage
\begin{thebibliography}{10}

\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

@@

@@

\bibitem{vrugt2008}
\bibinfo{author}{Vrugt, J.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Accelerating markov chain monte carlo simulation by
  differential evolution with self-adaptive randomized subspace sampling}.
\newblock \bibinfo{type}{Tech. Rep.}, \bibinfo{institution}{Citeseer}
  (\bibinfo{year}{2008}).

@@

>>>>

Dengue is an arthropod-borne febrile disease caused by a flavivirus with four 
serotypes which causes an estimated  $50$ million infections each 
year~\cite{Guzman2010}.
In humans, immunity against  a particular serotype is  considered permanent 
after the exposure and cross-immunity to the other serotypes is 
generally considered short lived~\cite{halstead_dengue_2007} although some 
studies argue for a longer duration of cross-immunity \cite{Reich2013, 
salje2012}.
As a consequence, the proportions of viral serotypes co-circulating at any 
point in time are strongly dependent on previous incidence patterns of the 
disease, which determine the number of individuals susceptible to each serotype 
at any point in time.
% LM: Maybe a citation here?

@@

\newpage
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

@@

\bibitem{Reich2013}
\bibinfo{author}{Reich, N.~G.} \emph{et~al.}
\newblock \bibinfo{title}{{{I}nteractions between serotypes of dengue highlight
  epidemiological impact of cross-immunity}}.
\newblock \emph{\bibinfo{journal}{J R Soc Interface}}
  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{20130414}
  (\bibinfo{year}{2013}).

\bibitem{salje2012}
\bibinfo{author}{Salje, H.} \emph{et~al.}
\newblock \bibinfo{title}{Revealing the microscale spatial signature of dengue
  transmission and immunity in an urban population}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{109}}, \bibinfo{pages}{9535--9538}
  (\bibinfo{year}{2012}).

@@

\bibitem{vrugt2008}
\bibinfo{author}{Vrugt, J.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Accelerating markov chain monte carlo simulation by
  differential evolution with self-adaptive randomized subspace sampling}.
\newblock \emph{\bibinfo{journal}{International Journal of Nonlinear Sciences
  and Numerical Simulation}} \textbf{\bibinfo{volume}{10}},
  \bibinfo{pages}{271--288} (\bibinfo{year}{2008}).

@@

\bibitem{mira2001}
\bibinfo{author}{Mira, A.}
\newblock \bibinfo{title}{On metropolis-hastings algorithms with delayed
  rejection}.
\newblock \emph{\bibinfo{journal}{Metron}} \textbf{\bibinfo{volume}{59}},
  \bibinfo{pages}{231--241} (\bibinfo{year}{2001}).
